---
title: "Interactive COVID-19 Report"
output: blastula::blastula_email
---

```{r, child=c('master_email.Rmd'), echo=FALSE, message=FALSE, warning=FALSE}

```
---

## A closer look at your area(s) of interest:

### Los Angeles County, CA

> `r email_body_func(la)`


#### 7-day moving average of new cases in Los Angeles County (`r min(la$date)` to `r max(la$date)`)

```{r echo=FALSE, warning=FALSE}
la <- mavg_plot_func(la)

la <-
  add_ggplot(plot_object = la)
la
```

---

### New York City, NY

> `r email_body_func(nyc)`


#### 7-day moving average of new cases in New York City (`r min(nyc$date)` to `r max(nyc$date)`)

```{r echo=FALSE, warning=FALSE}
nyc <- mavg_plot_func(nyc)

nyc <-
  add_ggplot(plot_object = nyc)
nyc
```

---

### Chicago (Cook County), IL

> `r email_body_func(ck)`


#### 7-day moving average of new cases in Chicago (Cook County) (`r min(ck$date)` to `r max(ck$date)`)

```{r echo=FALSE, warning=FALSE}
ck <- mavg_plot_func(ck)

ck <-
  add_ggplot(plot_object = ck)
ck
```


---

### Boston (Suffolk County), MA

> `r email_body_func(sf)`


#### 7-day moving average of new cases in Boston (Suffolk County) (`r min(sf$date)` to `r max(sf$date)`)

```{r echo=FALSE, warning=FALSE}
sf <- mavg_plot_func(sf)

sf <-
  add_ggplot(plot_object = sf)
sf
```

---

### Kansas City (Wyandotte County), Kansas

> `r email_body_func(kc)`


#### 7-day moving average of new cases in Kansas City (Wyandotte County), Kansas (`r min(kc$date)` to `r max(kc$date)`)

```{r echo=FALSE, warning=FALSE}
kc <- mavg_plot_func(kc)

kc <-
  add_ggplot(plot_object = kc)
kc
```


---

### Hong Kong

> `r email_body_func(hk)`


#### 7-day moving average of new cases in Hong Kong (`r min(hk$date)` to `r max(hk$date)`)

```{r echo=FALSE, warning=FALSE}
hk <- mavg_plot_func(hk)

hk <-
  add_ggplot(plot_object = hk)
hk
```


---

### Ontario, Canada

> `r email_body_func(tc)`


#### 7-day moving average of new cases in Ontario, Canada (`r min(tc$date)` to `r max(tc$date)`)

```{r echo=FALSE, warning=FALSE}
tc <- mavg_plot_func(tc)

tc <-
  add_ggplot(plot_object = tc)
tc
```

