---
title: "COVID-19 Report"
output: blastula::blastula_email
---


```{r echo=FALSE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse) # data manipulation and visualization
library(dplyr) # data manipulation
library(lubridate) # dates
library(data.table) # formatting 
library(knitr) # kniting 
library(ggplot2) # visualizations
library(matrixStats) # stats
library(plotly) # visualizations
library(purrr) # functional prog
library(expss) # format labeling 
library(zoo) # working w/time series data
library(blastula) #compose and send emails 
library(ggpubr) # setting multiple plots on one page
library(knitr) # knitting tables etc 
library(formattable) # awesome tables
library(viridis) # color palette
library(ggthemes) # themes for visuals
library(ggrepel)
library(rmarkdown)
library(usmap)
library(rio)

# # source functions, formats, data
source(here("scripts", "format.R"))
load(here("output", "loaded.Rdata"))
# #source("load_data.R")
source(here("scripts", "function.R"))

 
# Get a nicely formatted date/time string
date_time <- add_readable_time()

```


Hello:

This is your COVID-19 report, sent on `r date_time`. Shown below is a current **draft** in continual development and error checking. Please feel free to reach out with suggestions or issues! If you're curious about the situation in other places in the USA (state/county level) or international locations, please click [**here**](http://ec2-3-17-139-199.us-east-2.compute.amazonaws.com:3838/shiny_covid19_aws/).

---


### USA Overall

> `r usa_body`    

#### 7-day moving average of new cases in the US (`r first_day` to `r most_recent`)
```{r fig.align = "center", echo=FALSE, warning=FALSE, message=FALSE}

add_ggplot(plot_object = mavg_plot_func(daily_new))

```

### State Consecutive Day Trends 

> Of the 51 US states monitored, **`r state_metrics_cat_consec %>% filter(trend == "rising", days >= 7) %>% nrow()` (`r round(state_metrics_cat_consec %>% filter(trend == "rising", days >= 7) %>% nrow()/51 * 100, 2)`%) ** show consecutive increase in their 7-day moving average of new COVID-19 cases for at least 7 days. **`r state_metrics_cat_consec %>% filter(trend == "decreasing", days >= 7) %>% nrow()` (`r round(state_metrics_cat_consec %>% filter(trend == "decreasing", days >= 7) %>% nrow()/51 * 100, 2)`%)** show consecutive decrease for at least 7 days.
 
#### **`r state_metrics_cat_consec %>% filter(trend == "rising", days >= 7) %>% nrow()`** State(s) with Consecutive Increase for at least 7 days
<center>
```{r echo=FALSE, warning=FALSE, results='asis'}
table_consec_fun("rising")
```
</center>


####  **`r state_metrics_cat_consec %>% filter(trend == "decreasing", days >= 7) %>% nrow()`** State(s) with Consecutive Decrease for at least 7 days

<center>
```{r echo=FALSE, warning=FALSE, results='asis'}
table_consec_fun("decreasing")
```


### Region by Region 

How to read the maps below:    

*  **Cases Higher**: greater than or equal to 15 new cases per 100,000 people.   
*  **Cases Lower**: less than 15 new cases per 100,000 people.   
*  **Rising**: increase in the 7-day moving average, week over week.   
*  **Decreasing**: decrease in the 7-day moving average, week over week.  
*  **Staying**: no change in the 7-day moving average,  week over weeks

#### **Western US**

<center>
```{r echo=FALSE, warning=FALSE}
map_trend_func(west)
```
</center>

<center>
```{r echo=FALSE, warning=FALSE}
map_func(west)
```
</center>

#### **Southern US**

<center>
```{r echo=FALSE, warning=FALSE}
map_trend_func(south)
```
</center>

<center>
```{r echo=FALSE, warning=FALSE}
map_func(south)
```
</center>

#### **Midwestern US**
<center>
```{r echo=FALSE, warning=FALSE}
map_trend_func(midwest)

```
</center>

<center>
```{r echo=FALSE, warning=FALSE}
map_func(midwest)

```
</center>

#### **Northeastern US**
<center>
```{r echo=FALSE, warning=FALSE}
map_trend_func(northeast)
```
</center>

<center>
```{r echo=FALSE, warning=FALSE}
map_func(northeast)
```
</center>

  

### Other resources
Other resources to check out:

*  [See How All 50 States Are Reopening (and Closing Again)](https://www.nytimes.com/interactive/2020/us/states-reopen-map-coronavirus.html)
*  [NYtimes Visualizations for Case Tracking in U.S.](https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html)
*  [Coronavirus Drug and Treatment Tracker](https://www.nytimes.com/interactive/2020/science/coronavirus-drugs-treatments.html)
*  [Coronavirus Vaccine Tracker](https://www.nytimes.com/interactive/2020/science/coronavirus-vaccine-tracker.html)
*  [US Projections](https://covid19.healthdata.org/united-states-of-america?view=total-deaths&tab=trend)


---
